Deriving Multi-Headed Projective Dependency Parses \\ from Link Grammar Parses

### 2014-06-03 doc/LinksToDAG.tex

As recently discussed by \newcite{gomezrodriguez-nivre-2013}, one might impose various requirements on the parse graph:
\begin{itemize}

\item {\sc Single-Head}: each word has $\leq 1$ parent
\item {\sc Single-Head}: each word has at most one parent
\item {\sc Acyclic}: there are no directed cycles
\item {\sc Connected}: each pair of words has a undirected path between them
\item {\sc Reachable}: each word can be reached from 0 by a directed path
  \noteJE{note that this implies connected?  or does connected not allow 0 words on the path, i.e., does it restrict 0 to one child, and if not, is there a principle for that?  If no one, mention in footnote 1.}
\item {\sc Planar}: edges may not ``cross'' \\ (if there are edges between $u,v$ and between $i,j$, where $u < i < v$, then $u \leq j \leq v$)
\end{itemize}
It is common to impose all of these requirements at once, leading to a {\em projective dependency parser} that produces projective trees rooted at 0.\footnote{{\sc Projective} basically means {\sc Planar} + {\sc Reachable}.}  However, parsing algorithms can be devised that relax any or all of the requirements \cite{gomezrodriguez-nivre-2013}.

@@

%For our analysis of these parses, we further discarded those that had dropped words, where the link parser could not attach links to every word in the sentence. About \input{figure/conll_analysis_sentences_dropped}of the non-disconnected sentences were removed, leaving us working only with complete link parses.

>>>>

As recently discussed by \newcite{gomezrodriguez-nivre-2013}, one might impose various requirements on the parse graph:
\begin{itemize}[noitemsep]
\item {\sc Single-Head}: each word has $\leq 1$ parent
\item {\sc Acyclic}: there are no directed cycles
\item {\sc Connected}: each pair of words has a undirected path between them
\item {\sc Reachable}: each word can be reached from 0 by a directed path
  \noteJE{note that this implies connected?  or does connected not allow 0 words on the path, i.e., does it restrict 0 to one child, and if not, is there a principle for that?  If no one, mention in footnote 1.}
\item {\sc Planar}: edges may not ``cross'' \\ (if there are edges between $i,j$ and between $u,v$, where $i < u < j$, then $i \leq v \leq j$)
\end{itemize}
It is common to impose all of these requirements at once, leading to a {\em projective dependency parser} that produces projective trees rooted at 0.\footnote{{\sc Projective} basically means {\sc Planar} + {\sc Reachable}.}  However, parsing algorithms can be devised that relax any or all of the requirements \cite{gomezrodriguez-nivre-2013}.

@@

%For our analysis of these parses, we further discarded those that had dropped words, where the link parser could not attach links to every word in the sentence. About \input{figure/conll_analysis_sentences_dropped} of the non-disconnected sentences were removed, leaving us working only with complete link parses.
